%------------
% Ajjai Chandra - curriculum vitae
% Uses LaTeX and moderncv
%------------

%Setup
\documentclass[10pt,a4paper]{moderncv}
\usepackage{url}
\usepackage{footmisc}
\makeatletter
\usepackage[utf8]{inputenc}
\moderncvtheme[darkred]{classic}
\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.820]{geometry} % adjust the page margins
\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths

%Personal details.
\firstname{Ajjai}
\familyname{Chandra}
\nopagenumbers{}
\address{Chennai, India.}{}
\email{zencodes@ajjai.in}
\homepage{ajjai.in}

% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle
\section{Core Competencies}
\cvcomputer
{\textbf{Languages}}{Python, Haskell, C/C++, \\Golang, JavaScript}
{\textbf{Environment}}{Linux, Vim, Bash, Git, \\GNU toolchain, Docker}
\cvcomputer
{\textbf{Backends}}{Postgres, Redis, SQL}
{\textbf{The Web}}{Core Backend, HTML, Django, jQuery}
{\textbf{Traits}}{Core Backend, HTML, Django, jQuery}

% --------------------------------------
% WORK EX
% --------------------------------------

\section{Work Experience}

\cventry{Apr - Sep 2011}{{\href{http://www.google-melange.com/gsoc/project/google/gsoc2011/ajjairc/20001}{Google Summer of Code 2011}}}{Student Contractor}{Google}{}{Integrated SMARTS, a Game Artificial Intelligence Framework into KDE Gluon, and also implemented a KPart Graphical User Interface to plug the SMARTS Editor into Gluon.}

\cventry{July 2013 onwards}{{\href{http://tenmiles.com}{Tenmiles}}}{Software Developer}{at {\href{https://happyfox.com}{core, Happyfox Inc}}}{}{}

% --------------------------------------
% Courses
% --------------------------------------

\section{Education}
\cventry{2009 - 2012}{M.S in Information Technology (Masters)}{Wroclaw University of Technology, Wroclaw Poland}{}{}{\textit{CGPA $7.4$/$10.0$}. (Fall 2013 graduate)}
    \begin{itemize}
    {\item{1st semester - Wroclaw University of Technology, Poland}}
    {\item{2nd semester - Halmstad University of Technology, Sweden}}
    {\item{3rd semester - Aalborg University of Technology, Denmark}}
    {\item{4th semester - Wroclaw University of Technology, Poland}}
    {\item{Implemented W3C spec restrictions on WebIDL dictionary member types, among other patches.}}
    {}
\end{itemize}}
\cventry{2007 - 2008}{Advanced Diploma in Real Time Embedded System}{Cranes Institute - Diploma, Bangalore, Karnataka India}{}{}{\textit{CGPA $7.4$/$10.0$}. (Fall 2013 graduate)}
\cventry{2006}{B.Tech in Information Technology (Bachelors)}{Anna University, Chennai, Tamil Nadu India}{}{}{\textit{CGPA $7.4$/$10.0$}. (Fall 2013 graduate)}
\cventry{2013}{Thesis}{{\href{http://onloop.net/hairyplotter}{\small http://onloop.net/hairyplotter}}}{}{}{Human-Computer Interface with Electrooculogram-based eye gesture detection and classification.}
\cventry{2013}{Term Project}{{\href{http://onloop.net/hairyplotter}{\small http://onloop.net/hairyplotter}}}{}{}{Implementation of Elliptic Curve Cryptography}


\section{Open Source Contributions}

\cventry{Jan 2012 onwards}{{\href{https://bugzilla.mozilla.org/user\%5Fprofile?user\%5Fid=431664}{Mozilla}}}{}{}{}{
\begin{itemize}
{\item{Developed a Code Commenting/Uncommenting feature for the Mozilla Firefox Source Editor.}}
{\item{Implemented W3C spec restrictions on WebIDL dictionary member types, among other patches.}}
{}
\end{itemize}}

\cventry{July 2012}{{\href{https://github.com/mdoege/PySynth/commits?author=ajjairc}{PySynth}}}{}{}{}{Created an interactive Command Line Interpreter to parse Musical Notation and render tunes, aiding in on-the-fly notational composition with PySynth, and also implemented support for audio playback.}

% --------------------------------------
% PROJECTS
% --------------------------------------

\section{{\href{http://github.com/ajjairc/}{Independent Projects}}}

\cventry{}{Transit.js}{{\href{http://onloop.net/transit}{\small http://onloop.net/transit}}}{}{}{A JavaScript library to create purely client-side, interactive transit maps. The {{\href{http://onloop.net/chennairail}{Chennai Suburban Rail map}}} was created using transit.js.}

\cventry{}{Suburl}{{\href{http://u.onloop.net}{\small http://u.onloop.net}}}{}{}{A wildcard substitution-based URL Sanitizer/Shortener in Common Lisp.}

\cventry{}{This.onloop}{{\href{http://this.onloop.net}{\small http://this.onloop.net}}}{}{}{Music Search and Album discovery tool, with Common Lisp and Restas.}

\cventry{}{SC-ircle}{{\href{http://soundcloud.onloop.net}{\small http://soundcloud.onloop.net}}}{}{}{A Python/jQuery webapp to find out who among a Soundcloud user's followees aren't following them back; well-received by the spam-hit Soundcloud user community.}

\cventry{}{QuickHist}{{\href{http://quickhist.onloop.net}{\small http://quickhist.onloop.net}}}{}{}{An URL-based ASCII Histograms API using Common Lisp, Restas and CL-WHO.}

\cventry{}{Howstat}{{\href{http://redd.it/1i7lh3}{\small http://redd.it/1i7lh3}}}{}{}{Resident player-statistics lookup bot for Reddit's Cricket Community, {{\href{http://reddit.com/r/cricket}{/r/Cricket}}.}}

\cventry{}{PDoS}{{\href{http://music.onloop.net}{\small http://music.onloop.net}}}{}{}{Patterned Disruption of Silence - An exercise in extrapolating algorithmic patterns to musical notes.}

\cvitem{\textbf{Github}}{{\href{http://github.com/ajjairc}{\small github.com/ajjairc}}}
\end{document}
